CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-03-22 gpus/paper.tex
fix double fig
added more references

There are a number of descriptions of GPU-enabled astrophysical hydro
codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018,wang:2010,Padioleau2019,Bryan2014,Kulikov2014} \MarginPar{todo:
  group by AMR/no-AMR, GPU exclusive, Kokkos, ...}

>>>>

There are a number of descriptions of GPU-enabled astrophysical hydro
codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018,wang:2010,Padioleau2019,Bryan2014,Kulikov2014,Bedorf2012,Schive2018,Potter2016} \MarginPar{todo:
  group by AMR/no-AMR, GPU exclusive, Kokkos \citep{CarterEdwards2014}, ...}
